A Paucity of Young Stars and Planets in the Kepler Field

### 2024-06-05 paper/ms.tex
update ms

The right column of Figure~\ref{fig:hist_tgyro} compares our derived
age distribution against star formation histories (SFHs) reported by
\citet{2019A&A...624L...1M} and \citet{2020NatAs...4..965R} based on
CMD fitting.  The overall slope of both SFHs broadly agrees with what
we find from rotation-based ages.  The \citet{2019A&A...624L...1M}
data in particular are consistent, particularly after accounting for
the statistical uncertainties reported in that study.  Regarding the
episodic star formation bursts reported by
\citet{2020NatAs...4..965R}, they are not apparent in our overall FGK
star sample (top row).  However, rotation-based ages are most precise
for $\approx$G8V-K4V dwarfs older than $\approx$1.5\,Gyr
\citep{Bouma_2023}.  The lower row of Figure~\ref{fig:hist_tgyro}
selects these stars with a temperature cut, and may show a hint of the
$\approx$2\,Gyr spike reported by \citet{2020NatAs...4..965R}.  The
$\approx$1\,Gyr spike however is not recovered.  This
$\approx$2.5\,Gyr local maximum is similarly present in the isochrone
ages derived by \citet{Berger_2020a_catalog} for the Kepler field, and
in the red giant asteroseismic ages derived by
\citet{SilvaAguirre2018}.  The main novelty of our ages relative to
those studies is their accuracy at $<$1\,Gyr.

>>>>

The right column of Figure~\ref{fig:hist_tgyro} compares our derived
age distribution against star formation histories (SFHs) reported by
\citet{2019A&A...624L...1M} and \citet{2020NatAs...4..965R} based on
CMD fitting.  The overall slope of both SFHs broadly agrees with what
we find from rotation-based ages.  The SFH from \citet{2019A&A...624L...1M}
seems entirely consistent, particularly after accounting for
the statistical uncertainties of that study.  Regarding the
episodic star formation bursts reported by
\citet{2020NatAs...4..965R}, they are not apparent in our overall FGK
star sample (top row).  However, rotation-based ages are most precise
for $\approx$G8V-K4V dwarfs older than $\approx$1.5\,Gyr
\citep{Bouma_2023}.  The lower row of Figure~\ref{fig:hist_tgyro}
selects these stars with a temperature cut, and may show a hint of the
$\approx$2\,Gyr spike reported by \citet{2020NatAs...4..965R}.  The
$\approx$1\,Gyr spike however is not recovered.  This
$\approx$2.5\,Gyr local maximum is similarly present in the isochrone
ages derived by \citet{Berger_2020a_catalog} for the Kepler field, and
in the red giant asteroseismic ages derived by
\citet{SilvaAguirre2018}.  The main novelty of our ages relative to
those studies is that they are accurate at $<$1\,Gyr.
